Relative parabolic factorizations of Chevalley groups

### 2015-07-31 paper.tex
Relative torus is relative elementary + small fixes

\subsection{Elementary subgroup}
Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
These elements satisfy the well-known Steinberg relations:
\begin{equation}\label{rel:add}
x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \end{equation} 
\begin{equation}\label{rel:CCF}
\left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}.
\end{equation}
The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.

For $\xi\in R^*$ set $w_\alpha(\xi) = x_\alpha(\xi) x_{-\alpha}(-\xi^{-1}) x_{\alpha}(\xi).$
If $\rk(\Phi)\geq 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
\begin{equation}\label{rel:R3}
w_\alpha(\xi) x_{\beta}(s) w_\alpha(\xi)^{-1} =
x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\xi^{-\langle\beta,\alpha \rangle} s\right),\quad \xi,s\in R.
\end{equation}
where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).

@@

For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $x_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup. 
The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
$$\EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I).$$

>>>>

\subsection{Elementary subgroup}
Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
These elements satisfy the well-known Steinberg relations:
\begin{align}
& x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
& \left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
\end{align} 
The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.

For $\varepsilon\in R^*$ set $w_\alpha(\varepsilon) = x_\alpha(\varepsilon) x_{-\alpha}(-\varepsilon^{-1}) x_{\alpha}(\varepsilon).$
If $\rk(\Phi)\geqslant 2$ the following relation is a consequence of \ref{rel:add}--\ref{rel:CCF}:
\begin{equation}\label{rel:R3}
w_\alpha(\varepsilon) x_{\beta}(\xi) w_\alpha(\varepsilon)^{-1} =
x_{\sigma\ssub{\alpha}\beta} \left(\eta_{\alpha, \beta}\cdot\varepsilon^{-\langle\beta,\alpha \rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R.
\end{equation}
where coefficients $\eta_{\alpha, \beta} = \pm 1$ (see~\cite[\S13]{VP} for more details on $\eta_{\alpha, \beta}$).

We also define $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w(-1)$. Then
\[ h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right),\quad \varepsilon\in R^*,\ \xi\in R. \]

@@

For a special subset of roots $S\subseteq \Phi$ we denote by $\U(S, I)$ the subgroup spanned by all $x_{\alpha}(s)$ for $s\in I$, $\alpha\in S$.
The subgroup $\U(\Sigma_J, I)$ is normalized by $\E(\Delta_J, R)$, hence the Minkowski product set $\EP_J(R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I)$ is a subgroup. 
The following two equalities will be referred to in the sequel as {\it Levi decomposition}: 
\[ \EP_J(R, I) = \U(\Sigma_J, I) \cdot \E(\Delta_J, R, I) = \E(\Delta_J, R, I) \cdot \U(\Sigma_J, I). \]

Denote by $\Hh(\Phi,R)$ the subgroup generated by all $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$. Then set
\[ \Hh(\Phi,R,I) = \Hh(\Phi,R)\cap\G(\Phi,R,I)=\langle h_\alpha(\varepsilon),\ \alpha\in\Phi,\ \varepsilon\in R^*\cap(1+I)\rangle. \]
\begin{lemma}
$\Hh(\Phi,R,I)\leqslant\E(\Phi,R,I)$.
\end{lemma}
\begin{proof}
Set $\varepsilon=1+s$, $s\in I$ and write
\begin{multline*}
h_\alpha(1+s) = x_\alpha\left(-1\middle)\, x_{-\alpha}\middle(-s\middle)\, x_\alpha\middle((1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right) = \\
= x_\alpha\left((1+s)^{-1}-1\middle)\, z_{-\alpha}\middle(-s,(1+s)^{-1}\middle)\, x_{-\alpha}\middle(s(1+s)\right).
\end{multline*}
It remains to note that $(1+s)^{-1}\in 1+I$ and so all the factors lie in $\E(\Phi,R,I)$.
\end{proof}
